\documentclass[11pt,a4paper]{moderncv}

% moderncv themes
%\moderncvtheme[blue, roman]{casual}
% optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
\moderncvtheme[blue]{classic}                % idem

\usepackage[utf8]{inputenc}

% adjust the page margins
\usepackage[scale=0.8]{geometry}
\recomputelengths                             % required when changes are made to page layout lengths

% personal data
\firstname{Yiqun}
\familyname{Wang}
\title{}
\mobile{+86 13390782526}
\email{wyqqrince@gmail.com}
%% \quote{``Do what you fear, and the death of fear is certain.''\\-- Anthony Robbins}

%\phone{(312) 413-8265}                      % optional, remove the line if not wanted
%\fax{312 996 1491}                          % optional, remove the line if not wanted
%\photo[64pt]{avatar.jpg}                         % '64pt' is the height the picture must be resized to and 'picture' is the name of the picture file;

\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page

%% \renewcommand*{\sectionfont}{\LARGE\sffamily\monospace\slshape}
%% \renewcommand*\addressfont{\fontfamily{pzc}\selectfont}
%% \renewcommand*\sectionfont{\fontfamily{pzc}\fontsize{20}{24}\selectfont}

\begin{document}
\maketitle

\section{Education}
\cventry{2014--Present}{MS in Computer Science}{}{Supervisor: Xiaoxing Ma}{Nanjing University}{expected 2017}
\cventry{2010--2014}{BS in Computer Science}{Nanjing University}{}{}{}

\section{Internship Experience}

\cventry{2014.6-2014.9}
{Microsoft}
{Android}
{Bing Search on Android}{}
{
Learn Android from scratch, try to participate in project as soon as possible. During internship, I am in charge of some basic features, such as integrating voice SDK, image annotation, extension of browser etc. Besides, I have good communications with colleagues, including other developers, testers, PMs and designs. I can deliver results with high quality in short time.
}

\section{Project Experience}
%% \subsection{Research Projects}

\cventry{2014--present}
{Alloy Project}
{Java}
{Research Project}{}
{
This project aimed to use Alloy to verify the correctness of distributed controllers. Besides, a modular verification was proposed to accelerate the former verification. Then I leveraged Alloy to dealing with configuration management in cloud platform. For an application scenario, the project provided an verification in Alloy and a deployment using Chef api. I have been working on this project since 2014 all
by myself and the paper have been accepted to QRS '16.
}

\vspace*{0.2\baselineskip}

\cventry{2014--2015}
{ConUp Project}
{Java}
{Research Project}{}
{
Working with Guochao Ren, Dong Chen, Ping Su.\\
ConUp is implemented on top of Apache Tuscany, aimed to support dynamic deployment, management and online evolution of components. I mainly contributes to designing and developing the experiment part of ConUp which evaluates the performances of different algorithms.
}

\vspace*{0.2\baselineskip}

\cventry{2014}
{KRdecom Project}
{Java}
{Graduation Project}{}
{
An implementation of Krohn-Rhodes decomposition theorem. Besides developing, I also provide unit testing and function testing to guarantee the correctness of implementation, give an analysis of the algorithm's complexity and efficiency and verify them by experimental results.
}

\vspace*{0.2\baselineskip}


\section{Awards}
\cventry{2013}{National Scholarship}{}{}{}{}
\cventry{2012}{Second Prize in China Undergraduate Mathematical Contest in Modeling}{}{}{}{}
\cventry{2012}{Tung OOCL Scholarship}{}{}{}{}

\section{Skills}
\cventry{Languages}{Java > C++ > C}{}{}{}{}
\cventry{English}{CET-6}{fluent in spoken and written English}{}{}{}

% \closesection{}                   % needed to renewcommands
% \renewcommand{\listitemsymbol}{-} % change the symbol for lists

%\section{Extra 1}
%\cvlistitem{Item 1}
%\cvlistitem{Item 2}
%\cvlistitem[+]{Item 3}            % optional other symbol

%\section{Extra 2}
%\cvlistdoubleitem[\Neutral]{Item 1}{Item 4}
%\cvlistdoubleitem[\Neutral]{Item 2}{Item 5}
%cvlistdoubleitem[\Neutral]{Item 3}{}

\end{document}
